Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-02-23 presub/coverletter.tex
Cover letter updated for submission.

\address{Will M. Farr\\School of Physics and Astronomy\\University of Birmingham\\Birmingham\\B15 2TT\\United Kingdom}

\begin{letter}
{Leslie Sage \\
l.sage@us.nature.com \\}

\opening{Dear Dr. Sage:}

Please find enclosed a submission for a Nature Letter titled ``Aldebaran~b's
temperate past uncovered in planet search data''.

@@

Should you be interested in publishing the paper in Nature, it will require some
minor reformatting.  It is currently about 3000 words in the main body, with
five display items; however many details currently in the main body can be
easily moved to the appendices / methods sections.  It also contains more
references than permitted in a Letter, but many of these can also be moved to
the Methods section and others can be eliminated if necessary.

Thank you for considering our submission. Please do not hesitate to contact me
with any questions.  Should you feel that our submission is not appropriate for
Nature, we would be happy to have it considered for Nature Astronomy.

>>>>

\address{Will M. Farr\\School of Physics and Astronomy\\University of Birmingham\\Birmingham\\B15 2TT\\United Kingdom\\\href{mailto:w.farr@bham.ac.uk}{\texttt{w.farr@bham.ac.uk}}}

\begin{letter}
{Fred Rasio \\
\href{mailto:ApJLFred@northwestern.edu}{\texttt{ApJLFred@northwestern.edu}}}

\opening{Dear Dr. Rasio:}

Please find enclosed a submission for an ApJ Letter titled ``Aldebaran~b's
temperate past uncovered in planet search data''.

@@

We would like to have this submission considered for a linked Letter+Supplement;
we have formatted it as one document, but the appendices are intended for the
Supplement.  It is not clear to us whether there are length limits still applied
to letters; the main body is currently about 4000 words, contains six figures
(two of which could be merged if necessary), and sixty references (this could be
reduced by moving some references to the Supplement if necessary).

Thank you for considering our submission. Please do not hesitate to contact me
with any questions.
